Lactate transport inhibition therapeutically reprograms fibroblast

### 2024-02-13 manuscript/manuscript.qmd
add NADP data

## Lactate transport inhibition signals through histone lactylation

@@

Recently,

## Lactate transport inhibition / redox stress section

We next examined whether MCT inhibition affects TGFβ-dependent signaling pathways. TGFβ activates both SMAD and non-SMAD signaling pathways. We found no impact of MCT inhibition on decreasing Smad3 or ERK phosphorylation in LFs 48 h following TGFβ stimulation (**Figure 5**).

Hypoxia-inducible factor 1α (HIF-1α) is activated in lung fibroblasts following TGFβ and is required for myofibroblast differentiation and experimental pulmonary fibrosis partly through activation of glycolysis [@goodwin2018]. We found maximal HIF-1α stabilization 6 h following TGFβ treatment. At this time point, MCT inhibition did not decrease HIF-1α (**Figure 5E-F**), rather, HIF-1α protein levels were increased with combined MCT1 and MCT4 inhibition.

>>>>

## Lactate transport inhibition may signal through histone lactylation

@@

Post-translational protein modification of histone lysine residues by lactylation has been identified as a novel mechanism of metabolic regulation of gene expression [@zhang2019a]. Given the increase in intracellular lactate following MCT4 inhibition, we measured H3 histone lactylation by immunoblot (**Figure 6I-J**). We found that inhibition of both MCT1 and MCT4 increased histone lactylation and may account for some of the transcriptional changes observed following these treatments.

## Lactate transport inhibition contributes to antioxidant defense

Lactate metabolism is closely coupled to cellular redox homeostasis through its metabolism by lactate dehydrogenases, which couple lactate oxidation to NADH production. Since prior studies have suggested that reactive oxygen species (ROS) are important for TGFβ-mediated gene expression, we next examined the impact of lactate transport inhibition on cellular redox homeostasis. Consistent with an increase in intracellular lactate, we observed a concomitant increase in intracellular NADH/NAD^+^ (**Figure 7A-C**).
